Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-07 2020/JPDC_MCO/2020_JPDC.tex
JPDC добавил перевод сносок

A detailed description of the GSA algorithm is given in Algorithm \ref{alg:1} (see also \cite{c6}). The inputs of the algorithm are the function to be minimized $f(y)$\footnote{ }, the search domain $D$ from (\ref{eq:2}), the reliability parameter $r > 1$, the required accuracy $\varepsilon > 0$ and the maximum permissible number of global search iterations $kmax$. The output of the algorithm is an estimate of the global minimum point $y_k^* =y(x_k^*)$, the value of the function to be minimized at this point $z_k^* =f(y_k^*)$  and the number of performed global search iterations $k$. In the course of calculations, the search information $A_k$\footnote{ } from (\ref{eq:13}) is used, which contains the points of previously performed global search iterations $x_i$, $1 \leq i \leq k$, ordered in ascending order, and the values of the function to be minimized $z_i=f(y(x_i))$, $1\leq i \leq k$.

>>>>

A detailed description of the GSA algorithm is given in Algorithm \ref{alg:1} (see also \cite{c6}). The inputs of the algorithm are the function to be minimized $f(y)$\footnote{In the context of this paper, $f(y)$ can be regarded as one of the functions of the set $F(y)$ from (\ref{eq:3}).}, the search domain $D$ from (\ref{eq:2}), the reliability parameter $r > 1$, the required accuracy $\varepsilon > 0$ and the maximum permissible number of global search iterations $kmax$. The output of the algorithm is an estimate of the global minimum point $y_k^* =y(x_k^*)$, the value of the function to be minimized at this point $z_k^* =f(y_k^*)$  and the number of performed global search iterations $k$. In the course of calculations, the search information $A_k$\footnote{The set $A_k$ should be regarded as the search information $A_k(j)$ from (\ref{eq:13}) obtained by minimizing only one function $f(y)$.} from (\ref{eq:13}) is used, which contains the points of previously performed global search iterations $x_i$, $1 \leq i \leq k$, ordered in ascending order, and the values of the function to be minimized $z_i=f(y(x_i))$, $1\leq i \leq k$.
